WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-11-19 ms.tex
Prior on psi matches between equation and text
Advanced Virgo has not yet started

The \acl{LIGO} (\acsu{LIGO}; \cite{AdvancedLIGOHarry,AdvancedLIGO}) and Virgo \cite{AdvancedVirgo} have just begun taking data \cite{LIGOObservingScenarios} in their `Advanced' configurations. They will ultimately increase their reach in volume within the local Universe by three orders of magnitude as compared to their initial configurations through 2010. They form the first parts of a sensitive global \ac{GW} detector network, to be later augmented by the Japanese KAGRA facility \cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India~\cite{LIGOIndia}.

@@

Finally, the prior is uniform in $-1 \leq \cos\iota \leq 1$ and $0 \leq \psi < 2\pi$.

>>>>

The \acl{LIGO} (\acsu{LIGO}; \cite{AdvancedLIGOHarry,AdvancedLIGO}) has just begun taking data \cite{LIGOObservingScenarios} in its `Advanced' configuration. The two \ac{LIGO} detectors will ultimately increase their reach in volume within the local Universe by three orders of magnitude as compared to their initial configurations through 2010. They form the first parts of a sensitive global \ac{GW} detector network, soon to be augmented by Advanced Virgo \cite{AdvancedVirgo} and later by the Japanese KAGRA facility \cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India~\cite{LIGOIndia}.

@@

Finally, the prior is uniform in $-1 \leq \cos\iota \leq 1$ and $0 \leq \psi < \pi$.
